D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-08 ootavacuous.tex
Update abstract
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	This paper goes further, adding temporal constraints from
	long-standing laws of physics and constraints on hardware
	architecture and design, thereby providing an informal
	proof that OOTA cannot occur in correctly constructed C++
	programs running on real-world systems.

	The result is that a correct per-execution-path C++ implementation
	necessarily preserves the semantic dependencies that prevent
	OOTA cycles from forming.
	Implementations that undertake complex cross-thread analysis
	still need to be careful.
\end{abstract}

@@

% @@@ TODO:
% Create nicer sdep-evaluation example based on cbmc.
% Add a "Tools" section to the real-world constraints section.
%	Note the inversion from compiler, and the ability to complain
%	when analysis cannot be carried out accurately.
% Update wording.
% Add more detail on blocking UB to "Aside on Undefined Behavior".

>>>>

	This paper goes further, adding temporal constraints from
	long-standing laws of physics and constraints on hardware
	architecture and design to demonstrate that OOTA cannot occur in
	correctly constructed C++ programs and correctly constructed C++
	implementations running on on real-world systems.
	This paper also looks at some tooling implicatoins of OOTA.
\end{abstract}

@@

% @@@ TODO:
% Add a "Tools" section to the real-world constraints section.
%	Note the inversion from compiler, and the ability to complain
%	when analysis cannot be carried out accurately.
% Update wording.
% Add more detail on blocking UB to "Aside on Undefined Behavior".
